


\subsection{Generic Stream Cipher Interface} \label{subsec:interface}


\hsg{page 5 starting}

\textbf{Decoupling ciphers from the encryption process.} To flexibly switch
between configurations in SwitchCrypt requires a generic cipher interface. This
is challenging given the variety of inputs required by various stream ciphers,
the existence of non-length-preserving ciphers, and other differences. We
achieve the required generality by defining independent storage units called
\emph{nuggets}; we borrow this terminology from prior work (see
\cite{StrongBox}) to easily differentiate our logical blocks (nuggets) from
physical drive and other storage blocks. And since they are independent, we can
use our interface to select any configuration to encrypt or decrypt any nugget
at any point.



One of the goals of SwitchCrypt is that we might use any stream cipher
regardless of its implementation details. Yet this is entirely non-trivial.
There are many cipher implementations that we might use with SwitchCrypt, each
with unique input requirements and output considerations. For instance, Salsa
and Chacha implementations require a certain IV and key size and handle
plaintext input through successive invocations of a single state update
function~\cite{Floodyberry}. Using OpenSSL's AES implementation in CTR mode
requires manually tracking the counter state and individual ciphertext blocks
are retrieved though corresponding function invocations~\cite{OpenSSL}.
Freestyle's reference implementation requires we calculate the extra space
necessary per nugget (due to ciphertext expansion) along with
configuration-dependent minimum and maximum rounds-per-block, hash interval, and
pepper bits~\cite{Freestyle}. HC-128 and other ciphers have similarly disparate
requirements.

Unlike prior work, SwitchCrypt must be able to encrypt and decrypt arbitrary
nuggets \emph{with any of these ciphers} at any moment with low overhead and
without tight coupling to any specific implementation detail. Hence, there is a
need for an interface that completely decouples cipher implementations from the
encryption/decryption process. Our novel cipher interface allows any stream
cipher to be integrated into SwitchCrypt without modifications to third-party
code, enabling normally incompatible ciphers to encrypt and decrypt arbitrary
nuggets. The ability for disparate cipher implementations to co-exist forms the
foundation for SwitchCrypt's ability to switch the system between different
cipher configurations in our tradeoff space efficiently and effectively.

To facilitate this, the Generic Stream Cipher Interface presents the
cryptographic driver with a single unified encryption/decryption model.
SwitchCrypt receives I/O requests from the operating system at the block device
level like any other device-mapper. These requests come in the form of either
reads or writes. When a read request is received, the OS hands SwitchCrypt an
offset and a length and expects a response with plaintext of that specific
length starting at that specific offset taken from the beginning of storage
(i.e. the BODY section; see \figref{backstore}). When a write request is
received, the OS hands SwitchCrypt an offset, a length, and a buffer of
plaintext and expects that plaintext to be encrypted and committed to storage
such that the plaintext is later retrievable given that same offset and length
in a future read request. These requests can either be handled together by a
single function or handled individually as distinct read and write operations,
each with different tradeoffs.

\begin{enumerate}
   \item \textbf{\texttt{xor\_interface}}\\\texttt{xor\_interface} executes
   independently of SwitchCrypt internals and treats encryption and decryption
   as the same operation. Implementations receive an integer offset $F$, an
   integer length $L$, a key buffer $K$ corresponding to the current nugget, and
   an empty $L$-length XOR buffer. SwitchCrypt expects the XOR buffer to be
   populated with $L$ bytes of keystream output from some stream cipher seeked
   to offset $F$ with respect to key $K$. The length of the key buffer will
   always be exactly what the cipher implementation expects, alleviating the
   burden of key management; similarly, the XOR buffer will be XOR-ed with the
   appropriate portion of nugget contents automatically, alleviating the burden
   of drive access and other tedious calculations. \\
   \item \textbf{\texttt{read\_interface}} and
   \textbf{\texttt{write\_interface}}\\
   Unlike \texttt{xor\_interface}, encryption and decryption are distinct
   concerns at this abstraction level. \\\texttt{read\_interface} handles
   decryption during reads. \\\texttt{write\_interface} handles encryption
   during writes. Implementations receive full access to SwitchCrypt internals,
   giving wrapper code complete control over the encryption and decryption
   process and allowing implementers to bypass parts of the nugget-based drive
   layout abstraction (i.e. BODY) if necessary. This comes at the cost of 1)
   significantly increased code complexity, as the implementer must perform
   certain I/O manually, distinguish between independent nuggets on the drive,
   determine what to encrypt or decrypt at what offset and when, when to commit
   which metadata and where and 2) potential performance implications, since
   SwitchCrypt must account for not having absolute control over its internal
   data structures during function invocation. For a cipher like Freestyle,
   configurations with lower minimum and maximum rounds per block may see a
   performance improvement here, while configurations with higher minimum and
   maximum rounds per block may see reduced performance.
\end{enumerate}

\hsg{still need to talk today with Bernard .. what really is happening here.}
