\begin{abstract}

Recent work on Full Drive Encryption shows that stream ciphers achieve
significantly improved performance over block ciphers while offering stronger
security properties. However, optimizing for performance often conflicts with
other key concerns like energy usage and encryption strength. In this paper we
present SwitchCrypt, a software mechanism that navigates the tradeoff space made
by balancing competing security and latency requirements via \emph{cipher
switching} in space or time. We implement SwitchCrypt on an ARM big.LITTLE
mobile processor and test its performance under the popular F2FS LFS. We provide
empirical results demonstrating the conditions under which different switching
strategies are optimal and explore four related cases. Across these cases, we
find that SwitchCrypt achieves at least 3.3x in total energy use reduction,
remaining within our energy budget, and a 1.6x to 4.8x reduction in I/O latency
when compared to static approaches.

\end{abstract}

\PUNT{Full Drive Encryption (FDE) is essential for security in modern computing
systems, especially mobile systems. Recent work with stream-cipher based FDE
shows significantly improved throughput over block cipher based FDE while
offering stronger security properties. This approach is ideal when the only
optimization target is throughput; however, optimizing for high throughput often
conflicts with other key concerns like energy usage and the cipher's security
properties.

In this paper, we show that using stream ciphers for FDE creates a large
tradeoff space that could be used to balance competing security and latency
requirements.  We then present SwitchCrypt, a software mechanism that enables
dynamic navigation of these tradeoffs via \emph{cipher switching}, which can be
done in space or time. The key insight in this approach is achieving
low-overhead switching by leveraging the overwrite-averse, append-mostly
behavior of the underlying solid-state storage to trade throughput or total
energy use for desired security properties. We implement SwitchCrypt on an ARM
big.LITTLE mobile processor and test its performance under the popular F2FS LFS.
We provide empirical results that demonstrate the conditions under which
different switching strategies would be optimal. We then study SwitchCrypt's
dynamic flexibility through four case studies where latency, energy, and desired
security properties change dynamically. We find that SwitchCrypt achieves at
least 3.3x in total energy use reduction, remaining within our energy budget,
and a 1.6x to 4.8x reduction in I/O latency in our cases when compared to static
approaches.}
