\section{Evaluation}\label{sec:evaluation}

\subsection{Experimental Setup}

We implement \SYSTEM{} on a Hardkernel Odroid XU3 ARM big.LITTLE system with
Samsung Exynos5422 A15 and A7 quad core CPUs at maximum clock speed, 2Gbyte
LPDDR3 RAM at 933 MHz, and an eMMC5.0 HS400 backing store running Ubuntu Trusty
14.04.6 LTS, kernel version 3.10.106.

The maximum theoretical memory bandwidth for this model is 14.9GB/s\@. Our
observed maximum memory bandwidth is 4.5GB/s.

\subsection{Experimental Methodology}

In this section we answer the following questions:

\begin{enumerate}
 \item Can \SYSTEM{} reach dynamic configuration points in the tradeoff space?
 \item What is the performance overhead of each cipher switching strategy?
 \item What is the metadata overhead of each cipher switching strategy?
 \item What switching strategy works best in which scenario? For which workload?
\end{enumerate}

\TODO{Evaluate switching strategies against themselves. Different workloads, different size, etc. Show that overhead is low. Show that performance is maintained.}

\TODO{Paper up until this point makes assertions about static, offline, not flexible. Evaluation shows flexibility.}

\TODO{Show the graph that demonstrates that we have a method to navigate this space.}

\TODO{What assertions were made? Show results that demonstrate this.}

\TODO{This stuff works. Next section, show usefulness in practical circumstances.}

\TODO{A point somewhere about when to use different strategies. List of concerns that determine when to switch to what and why.}
