\section{Evaluation}\label{sec:eval}

We implement \sys and our experiments on a Hardkernel Odroid XU3 ARM big.LITTLE
system with Samsung Exynos 5422 A15/A7 heterogeneous multi-processing quad core
CPUs at maximum clock speed, 2 gigabyte LPDDR3 RAM at 933 MHz, and an eMMC5.0
HS400 backing store running Ubuntu Trusty 14.04.6 LTS, kernel version 3.10.106.
Energy monitoring was provided by the Odroid's integrated INA-231 power sensors
polled every $\approx{260}$ milliseconds (not including noise/overhead).

We evaluate \sys using a Linux RAM disk (tmpfs). The maximum theoretical memory
bandwidth for this Odroid model is 14.9GB/s\@. Our observed maximum memory
bandwidth is 4.5GB/s. Using a RAM disk focuses the evaluation on the performance
differences due to different ciphers.

In each experiment below, we evaluate \sys on two high level workloads:
sequential and random I/O. In both workloads, a number of bytes are written and
then read (either 4KB, 512KB, 5MB, 40MB) 10 times. Each workload is repeated
three times for a total of 240 tests per cipher (720 runs per cipher
pair/ratios, explained below); 30 results per byte size, 120 results per
workload. Results are accumulated and the median is taken for each byte size.

When evaluating switching strategies, a finer breakdown in workloads is made
using a pre-selected pair of ciphers we call the {\em primary cipher
configuration} and {\em secondary cipher configuration}. \sys is initialized at
the primary configuration. Once we trigger a cipher switch, \sys moves towards
the secondary configuration via switching model.

The cipher switch is triggered according to a certain {\em ratio} of I/O
operations. For example: given 10 40MB read-write operations, we may write and
then read back 40MB 3 times using the primary cipher, initiate a cipher switch,
and then write and then read back (write-read) 40MB 7 times. This would be a 3:7
ratio. It follows that there are three ratios we use to evaluate \sys's
performance in this regard: 7:3, 5:5, and 3:7. Respectively, that is 7 file
write-read operation in the primary cipher for every 3 file write-read
operations in the secondary cipher (7:3), 7 file write-read operation in the
primary cipher for every other file write-read operation in the secondary cipher
(5:5), and 3 file write-read operations in the primary cipher for every 7 file
write-read operation in the secondary cipher (3:7).

To reason about the desirability of cipher configurations, we define the
{\em security vector}, R+R, as a vector consisting of a configuration's
relative rounds (Rounds) quantification and its ciphertext randomization
(Randomization) quantification defined in \cref{sec:des}. We define the norm
over this vector as the sum of its components. Hence, we consider a cipher
configuration ``stronger'' if it has higher ciphertext randomization and uses
more rounds, \ie has a higher normed R+R.

All experiments are performed with basic Linux I/O commands, bypassing system
caching.

In this section we answer the following questions:

\begin{enumerate}
  \item What shape does the cipher configuration tradeoff space take under our
  workloads? (\cref{subsec:eval-baseline})
  \item Can \sys achieve dynamic security/energy tradeoffs by reaching
  configuration points not accessible with prior work?
  (\cref{subsec:eval-dynamic})
  \item What is the performance and storage overhead of each cipher switching
  model? (\cref{subsec:eval-overhead})
\end{enumerate}


% =======================================================
\subsection{Switching Strategies Under Workloads}\label{subsec:eval-baseline}

\input{graphics/fig-eval-baseline}

\cref{fig:eval-baseline} shows the normalized relative rounds and
ciphertext randomization (normed R+R vector) versus median normalized latency
tradeoff between different stream cipher configurations for our sequential and
random I/O workloads. Trends for median hold when looking at tail latencies as
well. Each line represents one workload: 4KB, 512KB, 5MB, and 40MB respectively
(see legend). Each symbol represents one of our ciphers: ChaCha8, ChaCha20,
Freestyle Fast, Freestyle Balanced, and Freestyle Strong. Of the ciphers we
tested, those with higher rounds and higher ciphertext randomization
scores resulted in higher overall latency and increased energy use for I/O
operations. The relationship between these concerns is not always linear,
however, which exposes a rich tradeoff space.

Besides the 4KB workload, the shape of each workload follows a similar trend,
hence we will focus on 40MB and 4KB workloads going forward. Due to the overhead
of metadata management and the fast completion time of the 4KB workloads
(\ie{little time for amortization of overhead}), ChaCha8 and ChaCha20 take
longer to complete than Freestyle Fast. This advantage is not enough to make
Freestyle Balanced or Secure workloads complete faster than the ChaCha variants,
however.

Though ChaCha8 is faster than ChaCha20, there is some variability in our timing
setup when capturing extremely fast events occurring close together in time.
This is why ChaCha8 sometimes appears with higher latency than ChaCha20 for
normalized 4KB workloads. ChaCha8 is not slower than ChaCha20.


% =======================================================
\subsection{Reaching Between Static Configurations}\label{subsec:eval-dynamic}

\input{graphics/fig-eval-forward}

\cref{fig:eval-forward} shows the normalized relative rounds and ciphertext
randomization (normed R+R vector) versus median normalized latency tradeoff
between different stream ciphers for our sequential and random I/O workloads
with cipher switching using the Forward model. After a certain number of
write-read I/O operations, a cipher switch is initiated and \sys begins using
the secondary cipher to encrypt and decrypt data. For each pair of ciphers, this
is repeated three times: once at every ratio point {\em between} our static
configuration points (\ie{7:3, 5:5, and 3:7 described above}).

The point of this experiment is to determine if \sys can effectively transition
the drive between ciphers without devastating performance. For the 40MB, 5MB,
and 512KB workloads (40MB is shown), we see that \sys can achieve dynamic
security/energy tradeoffs reaching points not accessible with prior work, all
with minimal overhead.

Again, due to the overhead of metadata management for non-Freestyle ciphers (see
\cref{sec:impl}) and the fast completion time of the 4KB workloads preventing
\sys from taking advantage of amortization, ChaCha8 and ChaCha20 take longer to
complete than Freestyle Fast for 4KB reads. We also see very high latency for
ratios between Freestyle Fast and Freestyle Strong cipher configurations. This
is because Freestyle is not length-preserving, so extra write operations must be
performed, and the algorithm itself is generally much slower than the ChaCha
variants (see \cref{fig:eval-baseline}). Doubly invoking Freestyle in a ratio
configuration means these penalties are paid more often.

\input{graphics/fig-eval-ms}

\cref{fig:eval-ms} show the performance of the Mirrored and Selective strategies
with the same configuration of ratios as \cref{fig:eval-forward}.

For the 40MB, 5MB, and 512KB workloads (40MB is shown), we see that Mirrored and
Selective {\em read} workloads and the Selective {\em write} workload achieve
parity with the Forward model experiments. This makes sense, as most of the
overhead for Selective and Mirrored reads is determining which part of the drive
to commit data to. The same applies to Selective writes. For the 4KB Mirrored
and Selective {\em read} workloads and the Selective {\em write} workload, we
see behavior similar to that in \cref{fig:eval-forward}, as expected.

Mirrored writes across all workloads are very slow. This is to be expected,
since the data is being mirrored across all areas of the drive. In our
experiments, the drive can be considered partitioned in half. This overhead is
most egregious for the 4KB Mirrored write workload. This makes Selective
preferable to Mirrored. However, it is a tradeoff; Selective cannot quickly
converge the drive to a single cipher configuration or survive the loss of an
entire region.


% =======================================================
\subsection{Cipher Switching Overhead}\label{subsec:eval-overhead}

We calculate that Forward switching has average overhead at 0.08x/0.10x for
40MB, 5MB and 512KB read/write workloads compared to baseline I/O, demonstrating
\sys's amortization of cipher switching costs. Average overhead is\\0.38x/0.44x
for 4KB read/write workloads when \sys is unable to amortize cost. There is no
spatial overhead with the Forward switching model.

Similarly, we calculate that Selective switching has average overhead at 0x/0.3x
for 40MB, 5MB and 512KB read/write workloads compared to baseline I/O. Average
overhead is 0.22x/0.71x for 4KB read/write workloads. Spatial overhead in our
experiment was half of all writable space on the drive.

Finally, we calculate that Mirrored switching has average overhead at
0.25x/0.61x for 40MB, 5MB and 512KB read/write workloads compared to baseline
I/O, with high write latency due to mirroring. Average overhead is 0.55x/0.77x
for 4KB read/write workloads. Spatial overhead in our experiment was half of all
writable space on the drive.

These overhead numbers are the penalty paid for the additional flexibility of
being able to reach configurations points that are unachievable without \sys.
\sys's design keeps these overheads acceptably low in practice, achieving the
desired goal of flexibly navigating latency/security tradeoffs for FDE.
