\begin{abstract}

\TODO{\\
    This.\\
    This.\\
    This.\\
    This.\\
    This.\\
    This.\\
    This.\\
    This.\\
    This.\\
    This.\\
    This.\\
    This.\\
    This.\\
    This.
}

\PUNT{ Recent work on Full Drive Encryption shows that stream ciphers achieve
significantly improved performance over block ciphers while offering stronger
security guarantees. However, optimizing for performance often conflicts with
other key concerns like energy usage and desired security properties. In this
paper we present \sys, a software mechanism that navigates the tradeoff space
made by balancing competing security and latency requirements via {\em cipher
switching} in space or time. Our key insight in achieving low-overhead switching
is to leverage the overwrite-averse, append-mostly behavior of underlying
solid-state storage to trade throughput for reduced energy use and/or certain
security properties. We implement \sys on an ARM big.LITTLE mobile processor and
test its performance under the popular F2FS file system. We provide empirical
results demonstrating the conditions under which different switching models are
optimal through the exploration of \numCases case studies. In one study, where
we require the filesystem to react to a shrinking energy budget by switching
ciphers, we find that \sys achieves up to a 3.3x total energy use reduction
compared to a static approach using only the Freestyle stream cipher. In another
case, where we allow the user to manually switch between ChaCha20 and Freestyle
stream ciphers flexibly, we achieve a 1.6x to 4.8x reduction in I/O latency
compared to prior static approaches.}

\end{abstract}\vten
